Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-26 prop_letter.tex

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome of
a theory that is contextual depends upon whether compatible sets of
observables are measured together or separately; a non-contextual
theory gives the same results in either case.  A classic example of
the varying opinions on the impact of imprecision is the disagreement
between Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999}
on whether finite-precision measurements invalidate the spirit of the
Kochen-Specker
theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.
The Kochen-Specker theorem is in essence a mathematical statement
about contextuality, asserting that in a Hilbert space of dimension
$d \ge 3$, it is impossible to associate definite probabilities,
$\mu(P_i)= 0$ or $1$, with every projection operator~$P_i$, in such a
way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$.  Meyer showed that one {\it can\/} assign
definite probabilities $0$ or~$1$ to the measurement outcomes when the
Hilbert space is defined over the field of rational numbers, therefore
nullifying the theorem~\citep{PhysRevLett.83.3751}.  However, Mermin
then argued that measurement outcomes must depend smoothly on slight
changes in the experimental configuration, leading him to assert that
the impact of Meyer's negative result is
``unsupportable''~\citep{Mermin1999}.  The debate on whether
contextuality is consistent with experimental outcomes continues to be
an active topic of
research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

>>>>

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome of
a theory that is contextual depends upon whether compatible sets of
observables are measured together or separately; a non-contextual
theory gives the same results in either case.  A classic example of
the varying opinions on the impact of imprecision is the disagreement
between Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999}
on whether finite-precision measurements invalidate the spirit of the
Kochen-Specker
theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.
The Kochen-Specker theorem is in essence a mathematical statement
about contextuality, asserting that in a Hilbert space of dimension
$d \ge 3$, it is impossible to associate definite probabilities,
$\mu(P_i)= 0$ or $1$, with every projection operator~$P_i$, in such a
way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$.  Meyer showed that one {\it can\/} assign
definite probabilities $0$ or~$1$ to the measurement outcomes when the
Hilbert space is defined over the field of rational numbers, therefore
nullifying the theorem~\citep{PhysRevLett.83.3751}.  However, Mermin
then argued that measurement outcomes must depend smoothly on slight
changes in the experimental configuration, leading him to assert that
the impact of Meyer's negative result is
``unsupportable'' on physical grounds~\citep{Mermin1999}.  The debate on whether
contextuality is consistent with experimental outcomes continues to be
an active topic of
research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
